Scale Space Edge Detection

### 2018-03-10 paper.tex
done

\section{Introduction}
Detecting edges in images has long been a persistent problem in image processing.  
Generally speaking, the majority of algorithms usually detect edges by identifying at least one of the following features:
\begin{itemize}
\item large discontinuities in luminance values
\item discontinuities in different object orientations
\item large discontinuities in the intensity gradient
\end{itemize}
In this paper, we will be using the scale space representation of an image to approach the edge detection problem.
Scale refers to how much smoothing is applied to the image. 
The theory behind the scale space representation is that detecting one-dimensional image features, like edges, may be dependent on what scale we operate at \cite{Lindeberg1998}. 
It follows that we can then define a scale space edge as a set of connected points that:
\begin{itemize}
\item have a gradient that assumes a local maximum value in the direction of the gradient\cite{Lindeberg1998}
\item have an edge strength metric which is a local maximum over various scales\cite{Lindeberg1998}.
\end{itemize}

\section{Motivation}
The motivation for this paper comes from observing how much the scale affects the detection of edges in an image. 
Most common edge detection algorithms are applied only at a scale of zero, i.e. the original image.
Common methods for detecting edges in images usually consist of convolving a discrete derivative matrix with the image to calculate spatial derivatives of the image.
Algorithms like the Sobel, Canny, Roberts, and Prewitt do just exactly that. 
The problem with these methods is that they are not very adaptable, and they could be possibly neglecting useful information at other scales. 
For example, given an image ${F}$, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
\begin{equation}
	{G}_x =
	\begin{bmatrix}
		+1 &0 &-1 \\
		+2 &0 &-2 \\
		+1 &0 &-1 
	\end{bmatrix}
	* {F}, \;
	{G}_y =
	\begin{bmatrix}
		+1 &+2 &+1 \\
		0 &0 &0 \\
		-1 &-2 &-1 
	\end{bmatrix}
	* {F}
\end{equation}
Our algorithm will consist of convolving the ando5 matrix, which is more rotationally symmetric than the other operators listed above, with the image. 
This convolution will be be performed at multiple scales to evaluate the criteria necessary for classifying a point as an edge point in the scale space. 
We then run a marching cubes algorithm to connect the local maxima and list our edges based on strength. 
The ability to list edges and classify their strengths is one of the advantages that the scale space edge algorithm has over conventional methods.

\section{Scale Space and Its Derivatives}
To understand how exactly we detect edges in the scale space, we must first define what the scale space is.
If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as the following convolution
\begin{equation}
  L(x,y;t) = g(x,y;t) * f(x,y)
\end{equation}
Here $t$ represents the scale parameter, and can be thought of how much smoothing is applied to the function. The function $g$ is the Gaussian kernel given by
\begin{equation}
  g(x,y;t) = \frac{1}{2 \pi t}e^{-(x^2+y^2)/(2t)}
\end{equation}
With the scale space representation defined, we can now take derivatives of it as it is a continuous well-defined function.
Spatial derivatives are relatively simple being defined as the following
\begin{equation}
  L_{x^{\alpha}y^{\beta}}(\cdot;t) = \partial_{x^{\alpha}y^{\beta}}L(\cdot;t) = g_{x^{\alpha}y^{\beta}}(\cdot;t) * f(\cdot)
\end{equation}
However, when taking the partial derivative with respect to the scale $t$, it becomes more interesting.
The scale space representation collection is a solution for the diffusion equation. Therefore is has the useful property of \cite{Lindeberg1993}
\begin{equation}
  \partial_t L = \frac{1}{2} \nabla^2 L = \frac{1}{2} (\partial_{xx} + \partial_{yy})L
\end{equation}
with the initial condition of $L(x,y;0) = f(x,y)$.
So we can now represent scale derivatives as spatial derivatives.

@@

The scale space representation is still defined in a similar fashion.
The following is the discrete version of the scale space operating on the function $f(x)$
\begin{equation}
  L(x;t) = (T(\cdot;t) * f(\cdot))(x;t)
\end{equation}
In this expression, $T$ represents the discrete version of the Gaussian kernel and is further evaluated as \cite{Lindeberg1993}
\begin{equation}
  T(n;t) = e^{-t}I_n(t)
\end{equation}
where $I_n$ is the modified Bessel functions of integer order given by
\begin{equation}
  I_n(x) = i^{-n}J_{n}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+n+1)}\left(\frac{x}{2}\right)^{2m+n}
\end{equation}
Now that the one dimensional case is understood for the scale space, we can expand this to two dimensions.
After all, images are composed of two dimensions, so it makes sense that these operators can act on two dimensional functions.
The two dimensional scale space representation for discrete variables is given by the following
\begin{equation}
  L(x,y;t) = \sum_{m=-\infty}^{\infty}\sum_{n=-\infty}^{\infty}T(m;t)T(n;t)f(x-m,y-n)
\end{equation}
Even with the discrete case, the scale space representation must still satisfy the semidiscretized version of the diffusion equation.
Therefore by taking a scale derivative of the function we must have the following \cite{Lindeberg1993}
\begin{equation}
  \partial_t L = \frac{1}{2}((1-\gamma)\nabla^2_5L+\gamma\nabla^2_\times L)
\end{equation}
where $\gamma \in [0,1]$ is a hyperparameter and,
\begin{equation}
  (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} - 4f_{0,0}
\end{equation}
\begin{equation}
  (\nabla^2_\times f)_{0,0} = \frac{1}{2}(f_{-1,-1} + f_{-1,+1} + f_{+1,-1} + f_{+1,+1} - 4f_{0,0})
\end{equation}
Note that $f_{-1,1}$ represents $f(x-1, y+1)$. Now that we have defined what discrete scale spaces and their derivatives look like, we can start to define what an edge is.

\section{Defining an Edge in Scale Space}
A useful system to use when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as \cite{Lindeberg1998}
\begin{equation}
  \begin{pmatrix}
    \cos{\alpha} \\
    \sin{\alpha}
  \end{pmatrix}
  = \frac{1}{\sqrt{L_x^2+L_y^2}}
  \begin{pmatrix}
    L_x \\
    L_y
  \end{pmatrix}
  \Bigg|_{(x_0,y_0)}
\end{equation}
With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
\begin{align}
  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
\end{align}
So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. The results for $L_v$ can be found on page \pageref{t_v}. So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}
The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}
The results for $L_{vv}$ can be found on page \pageref{t_vv}.
The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
\begin{equation} \label{eq:c2}
  \begin{aligned}
    \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
    \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
  \end{aligned}
\end{equation}
Then (Eq. \ref{eq:c1}) in conjunction with (Eq. \ref{eq:c2}) form the necessary constraints for us to define an edge in the scale space.
Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.

@@

The first scale derivative of the gradient magnitude results are found on page \pageref{t_tgma}. 
Its calculations are as follows \cite{Lindeberg1998}
\begin{equation} \label{dtGl}
  \partial_t (G_{\gamma}L) = \gamma t^{\gamma-1}(L_x^2+L_y^2) + t^{\gamma}(L_x(L_{xxx}+L_{yyy})+L_y(L_{xxy} + L_{yyy}))
\end{equation}
Then the second scale derivative of the gradient magnitude results are found on page \pageref{t_ttgma}.
Its calculations are as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    \partial_{tt}(G_{\gamma}L) &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
     & \hspace{.5pt}+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
     & \hspace{.5pt}+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2\big) \\
     & \hspace{.5pt}+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
     & \hspace{.5pt}+ L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
  \end{aligned}
\end{equation}
Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by \cite{Lindeberg1998}
\begin{equation}
  G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, \dif s
\end{equation}
where $\dif s^2=\dif x^2+\dif y^2$.

@@

Now that we have found all scale space edges, it remains to select an ``interesting'' subset of them to display.
To do this, we rank the edges by their integrated edge strength as described in the Theory and take the first $n$ of them to be sufficiently important to display.
% TODO: fix this
\begin{lstlisting}
function edge_importance(edge)
    total = 0
    for (x, y, t) in edge
        total += sqrt(GL[x,y,t])
    end
    return total
end

@@

\section{Results}
\subsection{Diffuse and sharp edges in the same photo}
To demonstrate the results of our program, we will use the following test image.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_orig.jpg}
  \caption{Block test image}
  \label{block_orig}
\end{figure}

Here is the result of thresholding the gradient as calculated by the Sobel operator for this image:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/sobel_block.jpg}
  \caption{The edges of the block image according to the Sobel gradient}
  \label{block_sobel}
\end{figure}

In contrast, our edge detection algorithm produces the following result:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_final.png}
  \caption{The final output of our program on the block image}
  \label{block_final}
\end{figure}
The edge of the shadow is clearly present in the image, a clear improvement over the Sobel gradient of the image.
Unfortunately, the edge of the shadow is not a continuous path.
This is due to spurious fragmentation of the edge in our marching cubes algorithm due to our inability to resolve ambiguous situations.
We can see this by displaying the full set of edges:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_all_edges.png}
  \caption{All edges of the block image as detected by our program}
  \label{block_all_edges}
\end{figure}
In this image, we see that the full edge of the shadow is captured, although there are also many spurious images formed by structures in the background that we do not want to detect.

\subsection{Other results}
Subjectively, our results seem quite reasonable for the given inputs.
Further improvement can be made to fix spurious edge segmentation in the future.
\begin{table}[H]
  \caption{Results of running our program on other images}
  \label{t_vvv}
  \centering
  \tabulinesep=0.3em
  \begin{tabu}to \textwidth{X[c,m]X[c,m]}
    \toprule
    Original & Result\\
    \midrule
    \includegraphics[height=18em]{{{Images/lena/lena_orig}}} & \includegraphics[height=18em]{{{Images/lena/lena_final}}} \\
    \includegraphics[height=18em]{{{Images/mandrill/mandrill_orig}}} & \includegraphics[height=18em]{{{Images/mandrill/mandrill_final}}} \\
    \includegraphics[height=18em]{{{Images/peppers/peppers_orig}}} & \includegraphics[height=18em]{{{Images/peppers/peppers_final}}} \\
    \bottomrule
  \end{tabu}
\end{table}

@@

>>>>

\section{Introduction}
Detecting edges in images has been a common problem in image processing.  
Generally speaking, the majority of algorithms usually detect edges by identifying at least one of the following features:
\begin{itemize}
\item large discontinuities in luminance values
\item discontinuities in different object orientations
\item large discontinuities in the intensity gradient
\end{itemize}
In this paper, we will be using the scale space representation of an image to approach the edge detection problem.
Scale refers to how much smoothing is applied to the image. 
The theory behind the scale space representation is that detecting one-dimensional image features, like edges, may be dependent on what scale we operate at \cite{Lindeberg1998}. 
It follows that we can then define a scale space edge as a set of connected points that:
\begin{itemize}
\item have a gradient that assumes a local maximum value in the direction of the gradient\cite{Lindeberg1998}
\item have an edge strength metric which is a local maximum over various scales\cite{Lindeberg1998}.
\end{itemize}

\section{Motivation}
The motivation for this paper comes from observing how much the scale affects the detection of edges in an image. 
Most common edge detection algorithms are applied only at a scale of zero, i.e. the original image.
Common methods for detecting edges in images usually consist of convolving a discrete derivative matrix with the image to calculate spatial derivatives of the image.
Algorithms like the Sobel, Canny, Roberts, and Prewitt perform such an operation. 
The problem with these methods is that they are not very adaptable, and they could neglect useful information at other scales. 
For example, given an image ${F}$, the following computes the gradient of the image in the $x$ and $y$ direction using the Sobel operator
\begin{equation}
	{G}_x =
	\begin{bmatrix}
		+1 &0 &-1 \\
		+2 &0 &-2 \\
		+1 &0 &-1 
	\end{bmatrix}
	* {F}, \;
	{G}_y =
	\begin{bmatrix}
		+1 &+2 &+1 \\
		0 &0 &0 \\
		-1 &-2 &-1 
	\end{bmatrix}
	* {F}
\end{equation}
Our algorithm will consist of convolving the $5 \times 5$ matrix, which is more rotationally symmetric than the other operators listed above, with the image. 
This convolution will be be performed at multiple scales to evaluate the criteria necessary for classifying a point as an edge point in the scale space. 
We then run a marching cubes algorithm to connect the local maxima and list our edges based on strength.

\section{Scale Space and Its Derivatives}
To understand how edges are defined in scale space, we must first define what the scale space is.
If we have a continuous function of multiple variables such as $f(x,y)$, then we define the scale space representation of such a function as the following convolution
\begin{equation}
  L(x,y;t) = g(x,y;t) * f(x,y)
\end{equation}
Here $t$ represents the scale parameter, and can be thought of how much smoothing is applied to the function. The function $g$ is the Gaussian kernel given by
\begin{equation}
  g(x,y;t) = \frac{1}{2 \pi t}e^{-(x^2+y^2)/(2t)}
\end{equation}
With the scale space representation defined, we can now take derivatives of it as it is a continuous well-defined function.
Spatial derivatives are relatively simple being defined as the following
\begin{equation}
  L_{x^{\alpha}y^{\beta}}(\cdot;t) = \partial_{x^{\alpha}y^{\beta}}L(\cdot;t) = g_{x^{\alpha}y^{\beta}}(\cdot;t) * f(\cdot)
\end{equation}
However, when taking the partial derivative with respect to the scale $t$, it becomes more interesting.
The scale space representation collection is a solution for the diffusion equation. Therefore is has the useful property of \cite{Lindeberg1993}
\begin{equation}
  \partial_t L = \frac{1}{2} \nabla^2 L = \frac{1}{2} (\partial_{xx} + \partial_{yy})L
\end{equation}
with the initial condition of $L(x,y;0) = f(x,y)$.
So we can now represent scale derivatives as spatial derivatives.

@@

The scale space representation is still defined in a similar fashion.
The following is the discrete version of the scale space operating on the function $f(x)$
\begin{equation}
  L(x;t) = (T(\cdot;t) * f(\cdot))(x;t)
\end{equation}
In this expression, $T$ represents the discrete version of the Gaussian kernel and is further evaluated as \cite{Lindeberg1993}
\begin{equation}
  T(n;t) = e^{-t}I_n(t)
\end{equation}
where $I_n$ is the modified Bessel functions of integer order given by
\begin{equation}
  I_n(x) = i^{-n}J_{n}(ix) = \sum_{m=0}^{\infty}\frac{1}{m!\Gamma(m+n+1)}\left(\frac{x}{2}\right)^{2m+n}
\end{equation}
Now that the one dimensional case is understood for the scale space, we can expand this to two dimensions.
The two dimensional scale space representation for discrete variables is given by the following
\begin{equation}
  L(x,y;t) = \sum_{m=-\infty}^{\infty}\sum_{n=-\infty}^{\infty}T(m;t)T(n;t)f(x-m,y-n)
\end{equation}
Even with the discrete case, the scale space representation must still satisfy the semidiscretized version of the diffusion equation.
Therefore by taking a scale derivative of the function we must have the following \cite{Lindeberg1993}
\begin{equation}
  \partial_t L = \frac{1}{2}((1-\gamma)\nabla^2_5L+\gamma\nabla^2_\times L)
\end{equation}
where $\gamma \in [0,1]$ is a hyperparameter and,
\begin{equation}
  (\nabla^2_5f)_{0,0} = f_{-1,0} + f_{+1,0} + f_{0,-1} + f_{0,+1} - 4f_{0,0}
\end{equation}
\begin{equation}
  (\nabla^2_\times f)_{0,0} = \frac{1}{2}(f_{-1,-1} + f_{-1,+1} + f_{+1,-1} + f_{+1,+1} - 4f_{0,0})
\end{equation}
Note that $f_{-1,1}$ represents $f(x-1, y+1)$. Now that we have defined what discrete scale spaces and their derivatives look like, we can start to define what an edge is.

\section{Defining an Edge in Scale Space}
A useful system to use when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
Here we setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as \cite{Lindeberg1998}
\begin{equation}
  \begin{pmatrix}
    \cos{\alpha} \\
    \sin{\alpha}
  \end{pmatrix}
  = \frac{1}{\sqrt{L_x^2+L_y^2}}
  \begin{pmatrix}
    L_x \\
    L_y
  \end{pmatrix}
  \Bigg|_{(x_0,y_0)}
\end{equation}
With our angle defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
\begin{align}
  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
\end{align}
So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. The results for $L_v$ can be found on page \pageref{t_v}. So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}
The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}
The results for $L_{vv}$ can be found on page \pageref{t_vv}.
The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
\begin{equation} \label{eq:c2}
  \begin{aligned}
    \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
    \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
  \end{aligned}
\end{equation}
Then (Eq. \ref{eq:c1}) in conjunction with (Eq. \ref{eq:c2}) form the necessary constraints for us to define an edge in the scale space.
Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.

@@

The first scale derivative of the gradient magnitude results are found on page \pageref{t_tgma}. 
Its calculations are as follows \cite{Lindeberg1998}
\begin{equation} \label{dtGl}
  \partial_t (G_{\gamma}L) = \gamma t^{\gamma-1}(L_x^2+L_y^2) + t^{\gamma}(L_x(L_{xxx}+L_{yyy})+L_y(L_{xxy} + L_{yyy}))
\end{equation}
Then the second scale derivative of the gradient magnitude results are found on page \pageref{t_ttgma}.
Its calculations are as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    \partial_{tt}(G_{\gamma}L) &= \gamma(\gamma-1)t^{\gamma-2}(L_x^2+L_y^2) \\
     & \hspace{.5pt}+ 2\gamma t^{\gamma-1}(L_x(L_{xyy}+L_{xxx})+L_y(L_{xxy}+L_{yyy})) \\
     & \hspace{.5pt}+\frac{t^{\gamma}}{2}\big((L_{xxx}+L_{xyy})^2+(L_{xxy}+L_{yyy})^2\big) \\
     & \hspace{.5pt}+ L_x(L_{xxxxx}+2L_{xxxyy}+L_{xyyyy}) \\
     & \hspace{.5pt}+ L_y(L_{xxxxy}+2L_{xxyyy}+L_{yyyyy})\big)
  \end{aligned}
\end{equation}
Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by \cite{Lindeberg1998}
\begin{equation} \label{estr}
  G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, \dif s
\end{equation}
where $\dif s^2=\dif x^2+\dif y^2$.

@@

Now that we have found all scale space edges, it remains to select an ``interesting'' subset of them to display.
To do this, we rank the edges by their integrated edge strength as described in (Eq. \ref{estr}) and take the first $n$ of them to be sufficiently important to display.
% TODO: fix this
\begin{lstlisting}
function edge_importance(edge)
    total = 0
    for (x, y, t) in edge
        total += sqrt(GL[x,y,t])
    end
    return total
end

@@

\section{Results}
\subsection{Diffuse and sharp edges in the same photo}
To demonstrate the results of our program, we will use the following test image.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.36]{Images/block/block_orig.jpg}
  \caption{Block test image}
  \label{block_orig}
\end{figure}

Here is the result of thresholding the gradient as calculated by the Sobel operator for this image:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.36]{Images/block/sobel_block.jpg}
  \caption{The edges of the block image according to the Sobel gradient}
  \label{block_sobel}
\end{figure}

In contrast, our edge detection algorithm produces the following result:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.36]{Images/block/block_final.png}
  \caption{The final output of our program on the block image}
  \label{block_final}
\end{figure}
The edge of the shadow is clearly present in the image, a clear improvement over the Sobel gradient of the image.
Unfortunately, the edge of the shadow is not a continuous path.
This is due to spurious fragmentation of the edge in our marching cubes algorithm due to our inability to resolve ambiguous situations.
We can see this by displaying the full set of edges:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.36]{Images/block/block_all_edges.png}
  \caption{All edges of the block image as detected by our program}
  \label{block_all_edges}
\end{figure}
In this image, we see that the full edge of the shadow is captured, although there are also many spurious images formed by structures in the background that we do not want to detect.

\subsection{Other results}
Subjectively, our results seem quite reasonable for the given inputs.
Further improvement can be made to fix spurious edge segmentation in the future.
\begin{table}[H]
  \caption{Results of running our program on other images}
  \label{results}
  \centering
  \tabulinesep=0.3em
  \begin{tabu}to \textwidth{X[c,m]X[c,m]}
    \toprule
    Original & Result\\
    \midrule
    \includegraphics[height=18em]{{{Images/lena/lena_orig}}} & \includegraphics[height=18em]{{{Images/lena/lena_final}}} \\
    \includegraphics[height=18em]{{{Images/mandrill/mandrill_orig}}} & \includegraphics[height=18em]{{{Images/mandrill/mandrill_final}}} \\
    \includegraphics[height=18em]{{{Images/peppers/peppers_orig}}} & \includegraphics[height=18em]{{{Images/peppers/peppers_final}}} \\
    \bottomrule
  \end{tabu}
\end{table}

@@

Note all images here are normalized, so only relative differences within the same image are relevant.
